MP MetaAnalysis

### 2018-09-19 Paper_Analyses_sandbox.Rmd
updated Methods/Results

---
title: "MP MetaAnalysis Monolinguals"
author: "Christina Bergmann"
output: 
  pdf_document:
    toc: true
---
```{r Setup, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, tidy = TRUE, message = FALSE, error = TRUE)

@@

db_ET <- db_ET %>%
  mutate(age.C = (mean_age_1-mean(mean_age_1, na.rm=TRUE))/30.44) %>%
  filter(mean_age_months < 31, infant_type == "typical")

@@

# Descriptive data

The database contains data from `r length(unique(dat$short_cite))` papers. In the tables below, we provide more descriptive information.

The next table shows what type of publications were included in our meta-analysis
```{r DescriptivesPubtype, echo = FALSE}

@@

unique(youngest$short_cite)
youngest$cond_lab <- ifelse(youngest$condition == 1, "correct", "misp")
ggplot(youngest, aes(x=cond_lab, y = g_calc, color = cond_lab)) + geom_boxplot()

@@

@@

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g),show.legend=FALSE) + 
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")

@@

  jpeg(filename = "figures/AgeEffect_log.jpg", 
       width = 500, height = 300, units = "px")

@@

```{r VocabularyData}
vocab_info <- db_ET_correct %>%
  mutate(has_vocab = ifelse(!is.na(r_comprehension), "comprehension", 
                            ifelse(!is.na(r_production), "production", "none"))) %>%
  group_by(has_vocab) %>%
  summarize(count = n())

@@

@@

@@

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature), data = dat_f, random = ~collapse | short_cite)

@@

```{r DistractorType}

rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = db_ET_MP, random = ~ collapse | short_cite)

@@

sum_eff <- round(coef(summary(rma_TypeFeatures_Lang))[2,], 2)

@@

```{r PlotDistFamEffect_condition}

@@

fn <- subset(dat, object_pair=="familiar_novel")
min_fn <- min(mf$mean_age_1)
max_fn <- max(mf$mean_age_1)

@@

dat_age= db_ET_MP%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat_age, random = ~ collapse | short_cite)

sum_eff <- round(coef(summary(rma_Distractor))[2,], 2)

@@

fn <- subset(dat, object_pair=="familiar_novel")
min_fn <- min(mf$mean_age_1)
max_fn <- max(mf$mean_age_1)

@@

@@

```{r Location}
#table(db_ET_MP$mispron_location)

@@

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_Location <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location, data = db_ET_MPl, random = ~collapse | short_cite)

#summary(rma_Location)

aov.type <- anova(rma_Location)

sum_eff <- round(coef(summary(rma_Location))[2,], 2)

@@

@@

@@

#summary(rma_LocationCondition)

@@

dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial")

@@

```{r DistractorOverlap}

@@

```{r MPtype}
db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )

>>>>

---
title: "MP MetaAnalysis"
author: "Christina Bergmann"
output: 
  pdf_document:
    toc: true
---
```{r Setup, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, tidy = TRUE, message = FALSE, error = TRUE)

@@

db_ET <- db_ET %>%
  mutate(age.C = (mean_age_1-mean(mean_age_1, na.rm=TRUE))/30.44) %>%
  filter(mean_age_months < 31)

@@

# Forest Plot

```{r ForestPlot}

#https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-met#a-analysis/

#Rename a bunch of things for ease

f.dat <-
  dat %>% 
  rename(cite = short_cite,
         yi = g_calc,
         vi = g_var_calc)

#Reorder bibliographic info based on value of g (yi), so effect sizes can be plotted in descending order

f.dat <-
  f.dat %>% 
  select(cite, expt_num, same_infant, mean_age_1, yi, vi, condition) %>% 
  mutate(study_ref = paste(cite, expt_num, same_infant, sep=',')) %>% 
  arrange(desc(yi))

f.dat$condition_label <- ifelse(f.dat$condition==1, "Correct", "Mispronunciation")

#Get standard errors from variances
f.dat$se = sqrt(f.dat$vi)

#Calculate 95% CI values
f.dat$lowerci = (-1.96*f.dat$se)+f.dat$yi
f.dat$upperci = (1.96*f.dat$se)+f.dat$yi

p <-  ggplot(f.dat, aes(y=reorder(study_ref, -yi), x=yi, xmin=lowerci, xmax=upperci, color = condition_label))+
  #Add f.data points and color them black
  geom_point()+
  #Add 'special' points for the summary estimates, by making them diamond shaped
#  geom_point(f.data=subset(f.dat, tester=='Summary'), color='black', shape=18, size=4)+
  #add the CI error bars
  geom_errorbarh(height=.1)+
  # set the colors to color blind
    scale_colour_manual(values=cbPalette)+
  #Specify the limits of the x-axis and relabel it to something more meaningful
  scale_x_continuous(limits=c(-1.5,1.5), name='Standardized Mean Difference (g)')+
  #Give y-axis a meaningful label
  ylab('Reference')+
  #Add a vertical dashed line indicating an effect size of zero, for reference
  geom_vline(xintercept=0, color='grey', linetype='dashed')+
  #Add a vertical line to show mean effect
  geom_vline(xintercept=0.91, color='black', linetype='dashed')+
    geom_vline(xintercept=0.25, color='blue', linetype='dashed')+
  #Create sub-plots (i.e., facets) based on levels of setting
  #And allow them to have their own unique axes (so authors don't redundantly repeat)
  #facet_grid(setting~., scales= 'free', space='free')+
  #Apply my APA theme
  apatheme+
      theme(text=element_text(family='Times', size=10),
            legend.position = "bottom",
            legend.title = element_blank())

  jpeg(filename = "figures/Forest_Plot.jpg", 
       width = 700, height = 600, units = "px")

# Methods

## Study Selection

The final sample (n = `r length(unique(dat$short_cite))`) consisted of `r with(dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(dat, n_distinct(short_cite[publication_status == "dissertation"]))` thesis, and `r with(dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports. We will refer to these items collectively as papers. Table X provides an overview of all papers included in the present meta-analysis.

```{r DescriptivesPubtype, echo = FALSE}

@@

unique(youngest$short_cite)
youngest$cond_lab <- ifelse(youngest$condition == 1, "Correct", "Mispronunciation")

ggplot(youngest, aes(x=cond_lab, y = g_calc, fill = cond_lab)) + 
    geom_boxplot() + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "none",
        axis.title.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")

  jpeg(filename = "figures/Youngest.jpg", 
       width = 500, height = 300, units = "px")

@@

### Plot Object Identification

```{r PlotObj_id}

p <- ggplot(dat, aes(condition_label, g_calc, fill = condition_label)) + 
  geom_boxplot() + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "none",
        axis.title.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")

  jpeg(filename = "figures/Object_ID.jpg", 
       width = 500, height = 300, units = "px")

@@

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g),show.legend=FALSE, alpha = .5) + 
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        text = element_text(size = 40)) + 
  xlab("Age in months") + 
  ylab("Hedges' g")

@@

  jpeg(filename = "figures/AgeEffect_log.jpg", 
       width = 700, height = 400, units = "px")

@@

```{r VocabularyData}
vocab_info <- db_ET_correct %>%
  mutate(has_vocab = ifelse(!is.na(r_comprehension), "comprehension", 
                            ifelse(!is.na(r_production), "production", "none"))) %>%
  group_by(has_vocab) %>%
  summarize(count = n(),
            papers = n_distinct(short_cite))

@@

```{r Vocab_describe1}
#how did vocabulary collection change over time?

dv <- read.csv("data/vocab_collection.csv", header = T)

years.v <- as.data.frame(seq(from = 2000, to = 2018, by = 1))
relat.v <- c("no_vocab", "no_relationship", "positive")

fake.v <- merge(years.v, relat.v, all = T)
names(fake.v) <- c("year", "relationship")
dat.v <- merge(dv, fake.v, by = c("year", "relationship"), all.y = T)
dat.v$vocab <- as.character(dat.v$vocab)
dat.v$relationship <- as.character(dat.v$relationship)
dat.v$short_cite <- as.character(dat.v$short_cite)

dat.v$vocab[is.na(dat.v$vocab)] <- "none"
dat.v$short_cite <- ifelse(dat.v$vocab == "none", "none", dat.v$short_cite)

dat.v$short_cite[is.na(dat.v$short_cite)] <- "none"

dat.v$tested <- ifelse(dat.v$short_cite == "none", "no", "yes")

vocab_data1 <- dat.v %>%
  group_by(year, relationship, tested) %>%
  summarize(count = n())

vocab_data1 <- as.data.frame(vocab_data1)
vocab_data1$count <- ifelse(vocab_data1$tested == "no", 0, vocab_data1$count)
vocab_data1$year <- as.numeric(vocab_data1$year)

vocab_data1$relationship <- ifelse(vocab_data1$relationship == "no_vocab", "None",
                                   ifelse(vocab_data1$relationship == "positive", "Predicts",
                                          "No Relationship"))
vocab_data1$relationship <- factor(vocab_data1$relationship, levels = c("Predicts", "No Relationship", "None"))

p <- ggplot(vocab_data1, aes(year, count, color = relationship)) + 
  geom_line() + 
  geom_point()+
  scale_y_continuous(breaks = c(0, 1, 2, 3, 4), limits = c(0,4))+
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom")
p

  jpeg(filename = "figures/Vocab_findings.jpg", 
       width = 500, height = 300, units = "px")

@@

### Number of infants and unique experimental conditions included in Features analysis

```{r NFeatures_demographics}

## Number of unique infants
infnum_info <- dat.f[,c("unique_ID", "same_infant", "expt_num", "n_1")]
infnum_info <- unique(infnum_info)

## Number of unique experimental conditions
condnum_info <- dat.f[,c("unique_ID", "same_infant", "expt_num", "expt_condition")]
condnum_info <- unique(condnum_info)

@@

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)

rma_NFeatures_agesub <- rma.mv(g_calc, g_var_calc, mods = ~as.numeric(n_feature), data = dat_f, random = ~collapse | short_cite)

@@

#### Correct condition

```{r DistractorType_correct}

rma_Distractor_correct <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = db_ET_correct, random = ~ collapse | short_cite)

#summary(rma_Distractor_correct)

aov.type <- anova(rma_Distractor_correct)

sum_eff <- round(coef(summary(rma_Distractor_correct))[2,], 2)

#### Mispronunciation condition

```{r DistractorType_misp}

rma_Distractor_MP <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = db_ET_MP, random = ~ collapse | short_cite)

@@

aov.type <- anova(rma_Distractor_MP)

sum_eff <- round(coef(summary(rma_Distractor_MP))[2,], 2)

@@

```{r PlotDistFamEffect_NoAge}

@@

s.plot <- ggplot(dat, aes(x= mean_age_1)) + 
  geom_bar(stat="count")+
  facet_grid(.~object_pair)

s.plot

fn <- subset(dat, object_pair=="familiar_novel")
min_fn <- min(fn$mean_age_1)
max_fn <- max(fn$mean_age_1)
mean_fn <- mean(fn$mean_age_1)
sd_fn <- sd(fn$mean_age_1)

ff <- subset(dat, object_pair=="familiar_familiar")
min_ff <- min(ff$mean_age_1)
max_ff <- max(ff$mean_age_1)
mean_ff <- mean(ff$mean_age_1)
sd_ff <- sd(ff$mean_age_1)

t.test(fn$mean_age_1, ff$mean_age_1)

@@

dat_age_MP= db_ET_MP%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

rma_Distractor_MP <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat_age_MP, random = ~ collapse | short_cite)

#summary(rma_Distractor_MP)

aov.type <- anova(rma_Distractor_MP)

sum_eff <- round(coef(summary(rma_Distractor_MP))[2,], 2)

# correct pronunciations
dat_age_correct= db_ET_correct%>%
  filter(mean_age_1>=min_age&mean_age_1<=max_age)

rma_Distractor_correct <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat_age_correct, random = ~ collapse | short_cite)

#summary(rma_Distractor_correct)

aov.type <- anova(rma_Distractor_correct)

sum_eff <- round(coef(summary(rma_Distractor_correct))[2,], 2)

@@

fn <- subset(dat, object_pair=="familiar_novel")
min_fn <- min(fn$mean_age_1)
max_fn <- max(fn$mean_age_1)

@@

### Object Recognition for Correct Pronunciations

```{r DistractorOverlap_correct}

db_ET_correctPo = db_ET_correct %>%
  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")

db_ET_correctPo$distractor_overlap <- factor(db_ET_correctPo$distractor_overlap, levels = c("onset", "no", "novel"))

rma_DistractorOverlap_correct <- rma.mv(g_calc, g_var_calc, mods = ~distractor_overlap, data = db_ET_correctPo, random = ~ collapse | short_cite)

#summary(rma_DistractorOverlap_correct)

aov.type <- anova(rma_DistractorOverlap_correct)

sum_eff1 <- round(coef(summary(rma_DistractorOverlap_correct))[2,], 2)
sum_eff2 <- round(coef(summary(rma_DistractorOverlap_correct))[3,], 2)

### Object Recognition for Mispronunciations

```{r DistractorOverlap_misp}

db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))

db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))

db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))

db_ET_MPo$condition_label <- ifelse(db_ET_MPo$condition==1, "Correct", "Mispronunciation")

db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))

db_ET_MPo$distractor_overlap <- factor(db_ET_MPo$distractor_overlap, levels = c("onset", "no", "novel"))

db_ET_MPo$condition_label <- ifelse(db_ET_MPo$condition==1, "Correct", "Mispronunciation")

@@

### Correct Object Recognition

```{r Location_correct}
#table(db_ET_MP$mispron_location)

db_ET_correctl = db_ET_correct %>%
  filter(mispron_location == "onset"  | mispron_location == "medial")

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_Location_correct <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location, data = db_ET_correctl, random = ~collapse | short_cite)

#summary(rma_Location_correct)

aov.type <- anova(rma_Location_correct)

sum_eff <- round(coef(summary(rma_Location_correct))[2,], 2)

### Mispronunciation Object Recognition

```{r Location_misp}
#table(db_ET_MP$mispron_location)

@@

#rma_NFeatures <- rma.mv(g_calc, g_var_calc, mods = ~as.ordered(n_feature), data = db_ET_MP, random = ~collapse | short_cite)
rma_Location_MP <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location, data = db_ET_MPl, random = ~collapse | short_cite)

#summary(rma_Location_MP)

aov.type <- anova(rma_Location_MP)

sum_eff <- round(coef(summary(rma_Location_MP))[2,], 2)

@@

# summary(rma_LocationCondition)

@@

db_ET_MPl = db_ET_MP %>%
  filter(mispron_location == "onset"  | mispron_location == "medial" | is.na(mispron_location))

db_ET_MPl$mispron_location <- as.character(db_ET_MPl$mispron_location)

db_ET_MPl$mispron_location <- ifelse(is.na(db_ET_MPl$mispron_location), "none", db_ET_MPl$mispron_location)

db_ET_MPl$mispron_location <- factor(db_ET_MPl$mispron_location, levels = c("none", "onset", "medial"))

@@

@@

dat.p = dat %>%
  filter(mispron_location == "onset"  | mispron_location == "medial")

@@

@@

```{r MPtype_descriptive}

cv_position <- db_ET_MP %>%
  group_by(type_feature, mispron_location) %>%
  summarize(count = n())

kable(cv_position)

family <- db_ET_MP %>%
  group_by(lang_family) %>%
  summarize(count = n())

kable(family)

cv_family <- db_ET_MP %>%
  group_by(type_feature, lang_family) %>%
  summarize(count = n())

kable(cv_family)

cv <- db_ET_MP %>%
  group_by(type_feature) %>%
  summarize(count = n())

kable(cv)

```{r MPtype}

db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )
